---
output: html_document
toc: True
toc_float: True
---

### Title: CUNY SPS MDS Data607_Assignmet3"
### Author: Charles Ugiagbe
### Date: "9/12/2021"

##            R Character Manipulation


##           Question 1

#1. Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS"

###   Load the required Packages
```{r}
library(tidyverse)
```

### Read file
This reads the file from github into a tibble (dataframe) and take a glimpse of the data
```{r}
url <- "https://raw.githubusercontent.com/omocharly/Data607_Assignment3/main/all-ages.csv"
college_majors <- read.csv(url)
head(college_majors)
```

```{r}
sub_filter <- dplyr::filter(college_majors, grepl('DATA|STATISTIC', Major))
sub_filter
```

```{r}
sub_col_majors <- sub_filter %>% select(Major_code:Employed)
sub_col_majors
```


##        Question 2

#2 Write code that transforms the data below:

[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"

[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  

[9] "elderberry"   "lime"         "lychee"       "mulberry"    

[13] "olive"        "salal berry"

Into a format like this:

c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")

##        solution 2

```{r}
library(stringr)
```

```{r}
main_data <- '[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"
[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  
[9] "elderberry"   "lime"         "lychee"       "mulberry"    
[13] "olive"        "salal berry"'
```

## output_string will return a list
```{r}
output <- str_extract_all(main_data, pattern = '[a-z]+\\s?[a-z]+')
output_string <- str_c(output, collapse = ", ")
```

```{r}
writeLines(output_string)
```


##        Question 3

#3 Describe, in words, what these expressions will match:

  *(.)\1\1
  *"(.)(.)\\2\\1"
  *(..)\1
  *"(.).\\1.\\1"
  *"(.)(.)(.).*\\3\\2\\1"


##        Solution 3

**(1)**   (.)\1\1
Matches strings containing any single character except new line followed by ‘\1\1’.

**(2)**   “(.)(.)\2\1”
Matches strings containing any two characters that are immediately followed by the same two characters in the opposite order. In essence, it matches a 4-character palindrome.

**(3)**   (..)\1
Matches strings containing any two characters (except new line) followed by ‘\1’.

**(4)**   “(.).\1.\1”
Matches strings containing any single character (except new line) followed by any character then the matched character followed by any character, then the matched character again.

**(5)**   "(.)(.)(.).*\3\2\1"
Matches strings containing any three characters in a row in which the three characters are repreated but in the opposite order later in the string.

### See examples to show usage of these strings


```{r}
example_1 <- c('a\1\1', 'b\1\1', 'ccc\1\1c', 'd\1d')
str_view(example_1, "(.)\1\1")
```

```{r}
example_2 <- c('abcccba', 'badmomdad', 'maddam')
str_view(example_2, "(.)(.)\\2\\1")
```

```{r}
example_3 <- c('abc\1d', 'abc\2dd', '\1d')
str_view(example_3, "(..)\1")
```

```{r}
example_04 <- c('philzlyl')
str_view(example_04, "(.).\\1.\\1")
```


##    Exercise 4 

Construct regular expressions to match words that:

*Start and end with the same character.*
Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)

##    solutios 4

```{r}
answer.str <- c("CHURCH","ELEVEN","PROP","SEVENTEEN","BANANA" ,"EAGLE")
```

### Word that start and end with the same character

```{r}
code1 <- "^(.).*\\1$"
answer.str %>% str_subset(code1)
```

### Word that contain a repeated pair of letters

```{r}
code2 <- "(..).*\\1"
answer.str %>% str_subset(code2)
```
### words that contain one letter in at least 3 places

```{r}
code3 <- "(.).*\\1.*\\1"
answer.str %>% str_subset(code3)
```

